Study guide: Algorithms and implementations for exponential decay models

### 2015-10-18 doc/src/chapters/alg/main_alg.tex
updates

% --- begin date ---
\begin{center}
Oct 10, 2015
\end{center}
% --- end date ---

@@

\subsection{Integer division}

@@

Solve the problem $u'=-au$, $u(0)=I$, using the Forward Euler, Backward
Euler, and Crank-Nicolson schemes. For each scheme, plot the error mesh
function $e^n = \uex(t_n)-u^n$ for $\Delta t$, $\frac{1}{4}\Delta t$, and
$\frac{1}{8}\Delta t$, where $\uex$ is the exact solution of the ODE and
$u^n$ is the numerical solution at mesh point $t_n$.

>>>>

% --- begin date ---
\begin{center}
Oct 17, 2015
\end{center}
% --- end date ---

@@

\subsection{Integer division}
\label{decay:py2}

@@

Solve the problem $u'=-au$, $u(0)=I$, using the Forward Euler, Backward
Euler, and Crank-Nicolson schemes. For each scheme, plot the error mesh
function $e^n = \uex(t_n)-u^n$ for $\Delta t=0.1, 0.05, 0.025$,
where $\uex$ is the exact solution of the ODE and
$u^n$ is the numerical solution at mesh point $t_n$.
